Tidy data structure to support exploration and modeling of temporal data

### 2018-12-01 main.Rmd
tweak paragraph in section index

Time provides a contextual basis for temporal data. Time representation could range from date-times (such as `POSIXct` and `Date` in R) to years, to sequential numbers for simulated data for example.

A variable representing time is indispensable to a tsibble, referred to as "index". The "index" is an intact data column rather than an attribute, which makes time accessible to users. It is highly advantageous when manipulating time. For example, one could easily extract time components, such as time of day and day of week, from the index to visualize seasonal effects of response variables. One could also join other data sources to the tsibble based on common time indices. The accessibility of tsibble index motivates data analysis towards transparency and human readability. But if the "index" is employed as attributes, analysts would write these simple queries in a programmatic manner, which can be avoidable from an analytic point of view.

A number of time classes are supported and easily extensible to new types. The baseline is that time indices can be potentially ordered from past to future. Characters cannot be ordered, so a variable hosting characters will make it unsupported for index. Ordered factors, however, can be immediately recognized as valid index. For instance, month names have a natural ordering from January to December, and so are weekdays from Monday to Sunday.

How to handle time zone. Additional representations are provided, like year-month, year-quarter. Extensible. Custom index classes can be supported.

@@

Tsibble supports an extensive range of index types from numerics to nano time, but there might be custom indices used for some occasions, for example school semesters. These academic terms vary from one institute to another within an academic year, which is defined differently from a calendar year. New index to be valid (defining `index_valid()`), the bottom line is that it can be ordered from past to future. The interval regarding semesters is further outlined through `pull_interval()`. As a result, the rest software methods such as `has_gaps()`, `count_gaps()` and `fill_gaps()` will have instant support for data that contains this new index.

>>>>

Time provides a contextual basis for temporal data. A variable representing time is indispensable to a tsibble, referred to as "index". The "index" is an intact data column rather than an attribute, which makes time accessible to users. It is highly advantageous when manipulating time. For example, one could easily extract time components, such as time of day and day of week, from the index to visualize seasonal effects of response variables. One could also join other data sources to the tsibble based on common time indices. The accessibility of tsibble index motivates data analysis towards transparency and human readability. But if the "index" is employed as attributes, analysts would write these simple queries in a programmatic manner, which can be avoidable from an analytic point of view.

Time representation could be arbitrary, for example R's native `POSIXct` and `Date` for versatile date-times, nano time for nanosecond resolution [@R-nanotime], and pure numbers in simulations. Yet ordered factors can also be a source of time, such as month names from January to December and weekdays from Monday to Sunday. New index classes are introduced to accurately represent year-week, year-month and year-quarter. Supporting a wide array of time types is a must for a tsibble, and extending for new types is a plus.

@@

Tsibble supports an extensive range of index types from numerics to nano time, but there might be custom indices used for some occasions, for example school semesters. These academic terms vary from one institute to another within an academic year, which is defined differently from a calendar year. New index would be immediately recognized by the software once `index_valid()` defined, as long as it can be ordered from past to future. The interval regarding semesters is further outlined through `pull_interval()`. As a result, the rest software methods such as `has_gaps()`, `count_gaps()` and `fill_gaps()` will have instant support for data that contains this new index.
